---
title: "sentimental analysis"
author: "Peiqi Jin UNI:pj2324"
date: "9/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##explore difference of happiness topic among people

##use key words from dictionaries in happyDB to find topics of each sentence

##step1:read the file and construct a dictionary for all topics
```{r}
hm_data <- read.csv("../output/processed_moments.csv")
entertainment<-"https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/entertainment-dict.csv"
exercise <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/exercise-dict.csv"
family <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/family-dict.csv"
food <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/food-dict.csv"
people <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/people-dict.csv"
pets <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/pets-dict.csv"
school <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/school-dict.csv"
shopping <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/shopping-dict.csv"
work <- "https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/topic_dict/work-dict.csv"

entertainment <- read.csv(entertainment, header=FALSE)
exercise <- read.csv(exercise, header=FALSE)
family <- read.csv(family,header=FALSE)
food <- read.csv(food, header=FALSE)
people <- read.csv(people, header=FALSE)
pets <- read.csv(pets, header=FALSE)
school <- read.csv(school, header=FALSE)
shopping <- read.csv(shopping, header=FALSE)
work <- read.csv(work, header=FALSE)

library(quanteda)

dic <- dictionary(list(entertainment=as.character(entertainment[, 1]), exercise=as.character(exercise[,1]),family=as.character(family[, 1]), food=as.character(food[, 1]), people=as.character(people[, 1]), pets=as.character(pets[,1]), school=as.character(school[, 1]), shopping=as.character(shopping[, 1]), work=as.character(work[, 1])))

```

## step2: use key words from dictionaries to find topics of each sentence

```{r}
hm_data$words <- lapply(as.character(hm_data$text), tokens)

lookup <- function(x){
  return(tokens_lookup(x, dic, valuetype=c("fixed"))$text1)
}

for(i in 1:nrow(hm_data)){
  hm_data$topics[i] <- list(lookup(hm_data$words[[i]]))
}
```



##step3: import the demographic file and combine hm_data with same id;
##delete repeated topics in the same sentence
```{r}
urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demo_data <- read.csv(urlfile)

library(dplyr)
library(tidyverse)
library(tidytext)
library(DT)
library(scales)
library(wordcloud2)
library(gridExtra)
library(ngram)
hm_data <- hm_data %>%
  inner_join(demo_data, by = "wid") %>%
  select(wid,
         original_hm,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         ground_truth_category, 
         words,
         topics) %>%
  mutate(topics=sapply(hm_data$topics, unique)) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(marital %in% c("single", "married")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_3 = "3m", hours_24 = "24h"))
```


## step 4: see topic frequencies among all people and visualized with wordcloud
```{r}
topic_count <- data.frame(table(unlist(hm_data$topics)))

library(wordcloud)

png("topiccloud.png")
wordcloud(topic_count$Var1, topic_count$Freq,
          scale=c(5,0.5),
          max.words=100,
          min.freq=1,
          random.order=FALSE,
          rot.per=0.3,
          use.r.layout=T,
          random.color=FALSE,
          colors=brewer.pal(9,"Blues"))
```




##step5(1): compare topic differences between male and female
```{r}
library(ggplot2)
hm_data_female <- hm_data %>%
  filter(gender %in% c("f"))
hm_data_male <- hm_data %>%
  filter(gender %in% c("m"))
df <- data.frame(table(unlist(hm_data_female$topics)))
dm <- data.frame(table(unlist(hm_data_male$topics)))
data1 <- cbind(df, dm[, 2])
colnames(data1) <- c("topic", "female", "male")
data1$female <- data1$female/nrow(hm_data_female)
data1$male <- data1$male/nrow(hm_data_male)

ggplot(data1, aes(female, male))+
  geom_point(aes(colour=factor(topic)), size=2)+
  geom_text(aes(label=topic), check_overlap = TRUE, size=2)+
  geom_abline(slope=1, intercept=0)
```

##step5(2):compare topic differences between married and single people
```{r}
hm_data_married <- hm_data %>%
  filter(marital %in% c("married"))
hm_data_single <- hm_data %>%
  filter(marital %in% c("single"))
dmar <- data.frame(table(unlist(hm_data_married$topics)))
dsin <- data.frame(table(unlist(hm_data_single$topics)))
data2 <- cbind(dmar, dsin[, 2])
colnames(data2) <- c("topic", "married", "single")
data2$married <- data2$married/nrow(hm_data_married)
data2$single <- data2$single/nrow(hm_data_single)

ggplot(data2, aes(married, single))+
  geom_point(aes(colour=factor(topic)), size=2)+
  geom_text(aes(label=topic), check_overlap = TRUE, size=2)+
  geom_abline(slope=1, intercept=0)
```


##step5(3):compare topic differences between parents and non-parents people
```{r}
hm_data_par <- hm_data %>%
  filter(parenthood %in% c("y"))
hm_data_nopar <- hm_data %>%
  filter(parenthood %in% c("n"))
dpar <- data.frame(table(unlist(hm_data_par$topics)))
dnop <- data.frame(table(unlist(hm_data_nopar$topics)))
data3 <- cbind(dpar, dnop[, 2])
colnames(data3) <- c("topic", "parent", "nopar")
data3$parent <- data3$parent/nrow(hm_data_par)
data3$nopar <- data3$nopar/nrow(hm_data_nopar)

ggplot(data3, aes(parent, nopar))+
  geom_point(aes(colour=factor(topic)), size=2)+
  geom_text(aes(label=topic), check_overlap = TRUE, size=2)+
  geom_abline(slope=1, intercept=0)
```



##step5(4):compare topic differences between 24hours and 3months reflection period
```{r}
hm_data_hour24 <- hm_data %>%
  filter(reflection_period %in% c("hours_24"))
hm_data_months3 <- hm_data %>%
  filter(reflection_period %in% c("months_3"))
dh24 <- data.frame(table(unlist(hm_data_hour24$topics)))
dm3<- data.frame(table(unlist(hm_data_months3$topics)))
data4 <- cbind(dh24, dm3[, 2])
colnames(data4) <- c("topic", "hours_24", "months_3")
data4$hours_24 <- data4$hours_24/nrow(hm_data_hour24)
data4$months_3 <- data4$months_3/nrow(hm_data_months3)

ggplot(data4, aes(hours_24, months_3))+
  geom_point(aes(colour=factor(topic)), size=2)+
  geom_text(aes(label=topic), check_overlap = TRUE, size=2)+
  geom_abline(slope=1, intercept=0)
```





